---
title: "Homework Assignment 1"
author: "Tao Wu"
output: pdf_document
date: "2026-01-23"
---

1. Write R code to do the following:
(a) Simulate a random number representing the number of shots that a basketball player makes in 10 tries, if the results of the shots are independent and she has a 40% chance of making each shot.

```{r}
set.seed(17) 
shots_made = rbinom(10, 1, 0.4)
sum(shots_made)
```

(b) Simulate a random number representing the number of shots that a basketball player makes in 10 tries, if the results of the shots are independent and her chance of making a shot is 10% for the first shot, 20% for the second shot, 30% for the third, etc.

```{r}

```

2. (a) Write R code to simulate 100 data points from a linear model with intercept 1, slope 2,
and residual standard deviation 3, where the predictors are sampled at random uniformly
from the range (0,4). Fit a linear regression to these data using lm, print the fitted model
using the display function from the arm package, and report whether the estimates of
the intercept and slope fall within 1 standard error of the true parameter values.
```{r}

```

(b) Fit the regression model using stan glm and print the results.
```{r}

```

(c) Write a Stan program, fit the model using the cmdstanr package, and print the results.
```{r}

```



